Can we predict the popularity of Netflix Shows?

### 2023-01-12 submission.Rmd
save work

---
title: Predicting Netflix Scores on Google 
author: Thalya Lim
# https://renkun.me/2022/03/06/my-recommendations-of-vs-code-extensions-for-r/
---

>>>>

---
title: Can we predict the popularity of Netflix Shows? 
author: Thalya Lim
Logo: <Put picture of Netflix logo>
output: 
    rmarkdown::html_document:
        theme: lumen
        highlight: rstudio
# https://renkun.me/2022/03/06/my-recommendations-of-vs-code-extensions-for-r/
# https://haozhu233.github.io/kableExtra/awesome_table_in_html.html
---

# About
This project is about analysing what makes a show on Netflix more likeable?

Are TV shows more well received than Movies?

Are action movies more popular than rom-coms?

Are shows from Korean more popular than Thai shows?

This project aims to answer such questions

# Data
* Main dataset is Netflix Dataset from Kaggle 
    + 8808 different titles, mix of TV series and movies, I will refer to both as shows
    + shows added from 2014-2021
    + shows released from 1925 up to 2021

```{r}
library(knitr)
library(kableExtra)
netflixData <- read.csv(file = 'datasets/dataset_main.csv')
temp = head(netflixData, 10)
temp %>%
  kbl() %>%
  kable_styling() %>%
  column_spec(1, width = "10cm") %>%
  scroll_box(width = "1000px", height = "500px")
```

* Review Scores and Supplementary info for each title scrapped from Google
+ To find the popularity of the show, the most important feature, we use the review how many people from Google likes it 
< Put picture of squid game with the review in google search >

```{r}
library(reticulate)
use_python("C:/venv/Scripts/python.exe")
use_virtualenv("C:/venv")
```

```{python}
import pandas as pd
import requests
import urllib
from requests_html import HTML
from requests_html import HTMLSession
import bs4

def get_source(url):
    """Return the source code for the provided URL. 
    Args: 
        url (string): URL of the page to scrape.
    Returns:
        response (object): HTTP response object from requests_html. 
    """

    try:
        session = HTMLSession()
        response = session.get(url)
        return response

    except requests.exceptions.RequestException as e:
        print(e)

def get_googleInfo(title):

    scrapedData = []

    query = urllib.parse.quote_plus(title)
    response = get_source("https://www.google.co.uk/search?q=" + query)

    soup = bs4.BeautifulSoup(response.text,"html.parser")

    rating_object=soup.find_all( "div", {"class":"a19vA"} )
    info_object=soup.find_all( "div", {"class":"rVusze"} )
    desc_object=soup.find_all( "div", {"class":"PZPZlf hb8SAc"} )

    scrapedData.append('Title: ' +title)

    for rating in rating_object:
        ratingInfo = rating.getText()
        rating = ratingInfo[0:3]
        scrapedData.append('Rating: ' +rating)

    for info in info_object:
        info = info.getText()
        if 'Language' in info:
            scrapedData.append(info)
            break

    for info in info_object:
        info = info.getText()
        if 'Genre' in info:
            scrapedData.append(info)
            break

    for desc in desc_object:
        description = desc.getText()
        description = description[0:11] + str(': ') + description[11:]
        scrapedData.append(description)
        break

    return scrapedData

# Test Function
info = get_googleInfo("Squid Game")
print(info)
```

Data Blending (header)
We blend the Main Kaggle dataset with the Google dataset
Using SQLite to join them, this gives us more versatility. Could've use the R joins but I feel most comfortable using SQL 
Some shows could not be google so we use a left join on the main dataset 
< show code from Data Cleaning.r >

Data Cleaning (header)
Renaming Features (sub-header)
+ id 
+ type
+ title
+ director
+ cast
+ country
+ date_added
+ release_year
+ rating
+ duration
+ genre
+ plot
+ score
+ google_language
+ google_genre
+ google_plot
< code >

Cleaning each feature (sub header) 
Look for inconsistencies, duplicates, outliers, etc. 
Changing type and formats
Recatagorize 
+ id - check completeness
+ type - summary 
+ title - check completeness
+ director - summary
+ cast - summary 
+ country - summary
+ date_added - 
+ release_year
+ rating
+ duration
+ genre
+ plot
+ score
+ google_language
+ google_genre
+ google_plot

Handle missing data (sub header)
Missing reviews (sub sub header)
Remove rows with no data on reviews
< code >

Analysing missing datapoints (sub sub header)
< code >
Pretty useless to have these features
But I transform the fields into present/absent
Just in case it has predictive capabilities
< code >
